CommonMind Consortium: DLPFC

### 2020-09-22 combined_analysis/diff.networks.Rmd
Update diff networks

rownames(df_schema2) = df_schema2$ENSEMBL
```

>>>>

rownames(df_schema2) = df_schema2$ENSEMBL

# ASD
df_asd = fread(synGet('syn22343811')$path)
colnames(df_asd)[colnames(df_asd)=="Q‑Val" ] = 'Q'
df_asd2 = data.frame(ENSEMBL = df_asd$Gene, Q = df_asd$Q)
df_asd2$chisq = qchisq(df_asd2$Q + 1e-15, 1, lower.tail=FALSE)
rownames(df_asd2) = df_asd2$ENSEMBL

```
